Microplatforms: Product platforms as code

### 2018-06-20 paper.tex
mods to infrastructure subsection

First let’s look at the significant features of this architecture.

@@

\bibliography{bibliography}
\bibliographystyle{plain}

>>>>

@@

The infrastructure provisioning is 100\% automated using Terraform scripts. The cluster configuration can be generated by Kops. By using Kops to output Terraform scripts (and overriding resource definitions as required), we can also use Terraform to provision the clusters, committing the code to github as we go. All infrastructure can be provisionied this way, and any infrastructure changes must be made by modifying, and re-applying, the scripts.
\bibliography{bibliography}
\bibliographystyle{plain}
